Spectral Variability of Two Rapidly Rotating Brown Dwarfs: \\2MASS~J08354256$-$0819237 and 2MASS~J18212815+1414010

### 2017-03-15 ms.tex
I added a reference to Hiranaka's results on the particle size distribution which are similar to our constraints for 2MASS 1821+1414

A similar amplitude versus wavelength trend was recently observed for WISEP J004701.06+680352.1 \citep{2016ApJ...829L..32L}, which has very red ($J-K$ = 2.55) spectral energy distribution thought to be caused by a high altitude haze layer.
In WISEP J0047, the wavelength trend could be fit by $\sim0.4~\mu$m forsterite grains, which is close to our characteristic particle size.

>>>>

A similar amplitude versus wavelength trend was recently observed for WISEP J004701.06+680352.1 \citep{2016ApJ...829L..32L}, which has very red ($J-K$ = 2.55) spectral energy distribution thought to be caused by a high altitude haze layer.
In WISEP J0047+6803, the wavelength trend could be fit by $\sim0.4~\mu$m forsterite grains, which is close to our characteristic particle size.

\citet{hiranaka2016subMicronDust} find that the observed spectra of reddened L dwarfs can be explained by extinction from a haze layer of sub-micron forsterite grains.
They find typical mean particle radii of 0.15 to 0.35 $\mu$m for a sample of L dwarf stars.
Our median particle radius of $r$=0.24 $\mu$m for \shb\ is consistent with this range and may represent a partially cloudy version of the reddened stars in \citet{hiranaka2016subMicronDust} or WISEP J0047+6803.
